### 2020-10-28 README.Rmd
Working on small example and documentation

@@

ex_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(census_df1_ex, census_df2_ex_no_r, id) %>%
  mutate(
    sp = to_any_case(sp),
    sp = as.factor(sp)) %>%
  # drop stemID
  select(-ID)

@@

set.seed(76)
#ex_cv_grid <- spatialBlock(
#  speciesData = ex_growth_df, theRange = 5, verbose = FALSE, k = 2
#)

# Add foldID to data
ex_growth_df <- ex_growth_df %>% 
  mutate(
    foldID = ex_cv_grid$foldID
  )

# Visualize grid. Why does fold 19 repeat?
ex_cv_grid$plots +
  geom_sf(data = ex_growth_df, aes(col=factor(foldID)), size = 1)

ex_cv_grid <- ex_cv_grid$blocks %>%
  st_as_sf()

>>>>

Need to write this up for the readme.

@@

ex_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(census_df1_ex, census_df2_ex_no_r, id) %>%
  mutate(
    sp = to_any_case(sp),
    sp = as.factor(sp))

@@

# Bert's solution: Manually create a blocks sf object
fold1 <- rbind(c(0, 0), c(5, 0), c(5, 5), c(0, 5), c(0, 0))
fold2 <- rbind(c(5, 0), c(10, 0), c(10, 5), c(5, 5), c(5, 0))
blocks <- bind_rows(
  sf_polygon(fold1),
  sf_polygon(fold2) ) %>%
  mutate(foldID = c(1, 2))

# Plot
ggplot() +
  geom_sf(data = ex_growth_df, aes(col = buffer), size = 2) +
  geom_sf(data = blocks, fill = "transparent")

# fit spatialBlock()
ex_cv_grid <- spatialBlock(
  speciesData = ex_growth_df,
  verbose = FALSE,
  k = 2,
  # Note new arguments
  selection = "systematic",
  blocks = blocks#,
 # foldsCol = "foldID"
)

# Add foldID to data
ex_growth_df <- ex_growth_df %>%
  mutate(foldID = ex_cv_grid$foldID %>% as.factor())

# Visualize grid
ex_cv_grid$plots +
  geom_sf(data = ex_growth_df, aes(col = foldID), size = 2)

# Deliverable
ggplot() +
  geom_sf(data = ex_growth_df, aes(col = foldID, shape = buffer))

ex_cv_grid_sf <- ex_cv_grid$blocks %>%
  st_as_sf()

# focal v comp
focal_vs_comp_ex <- ex_growth_df %>% 
  create_focal_vs_comp(max_dist, cv_grid_sf = ex_cv_grid_sf, id = "ID")

# fit the model
posterior_param_ex <- focal_vs_comp_ex %>% 
  fit_bayesian_model(prior_param = NULL, run_shuffle = FALSE)

# get predictions
predictions <- focal_vs_comp_ex %>%
  predict_bayesian_model(posterior_param = posterior_param_ex) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))
predictions %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)

# plot posteriors
posterior_param_ex %>%
  plot_posterior_parameters()

# run model with CV
ex_bw <- focal_vs_comp_ex %>% 
  run_cv(max_dist = max_dist, cv_grid = ex_cv_grid) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

ex_bw %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
